Modeling vertical-axis cross-flow turbine wakes

### 2015-07-24 paper.tex
Add cross-stream extent of the refined zone

Meshes were generated using \textit{OpenFOAM}'s \textit{blockMesh} and
\textit{snappHexMesh} utilities. Mesh topology consists of a background
hexahedral mesh, which is refined in all three directions by a factor of 2 in a
rectangular region containing the turbine and near-wake (0.9 m upstream, 1.3 m
downstream and $\pm$ 0.8 m vertically). Cells adjacent to the turbine shaft and
struts are refined by a factor of 4, while cells adjacent to the blades are
refined by a factor of 6. To capture the boundary layer, 20 layers are added
next to the blades with an expansion ratio of 1.2. Overall mesh refinement is
controlled by a single parameter---the number of cells in the streamwise
direction, $N_x$.

>>>>

Meshes were generated using \textit{OpenFOAM}'s \textit{blockMesh} and
\textit{snappHexMesh} utilities. Mesh topology consists of a background
hexahedral mesh, which is refined in all three directions by a factor of 2 in a
rectangular region containing the turbine and near-wake (0.9 m upstream, 1.3 m
downstream, $\pm$ 0.9 m cross-stream, and $\pm$ 0.8 m vertically). Cells
adjacent to the turbine shaft and struts are refined by a factor of 4, while
cells adjacent to the blades are refined by a factor of 6. To capture the
boundary layer, 20 layers are added next to the blades with an expansion ratio
of 1.2. Overall mesh refinement is controlled by a single parameter---the number
of cells in the streamwise direction, $N_x$.
